Supplementary Information

### 2021-03-13 doc/manuscript/ForestGEO_treerings.Rmd
rearrange results
move climate x DBH interactions under climate sensitivity section

#Figures
schematic=1
SCBI_example=2
clim_sens=3
size=4
interactions_fig = 5 #DBH/climate interactions
year_fig = 6

@@

*(insert content on additive effects?)*

@@

*(move this down after climate-DBH interactions?)*

![**Figure 4 | Growth sensitivity to DBH: (a) $RW$, (b) $BAI$, (c) $\Delta AGB$.** Relationships for species are plotted when included in the top model. Other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant.  Transparent ribbons indicate 95% confidence intervals.](tables_figures/DBH_responses.png)

## Additive and interactive effects of climate and DBH {-#Additive}

When a precipitation variable, a temperature variable, and $DBH$ were all included as candidate variables in the GLS models, typically all three were included in the top model, regardless of the growth metric used.
Climate responses were generally similar to those described above for models without a $DBH$ term, although some of the weaker climate responses were not consistently included in top models (e.g., $T_{min}$ responses at BCNM; Figs. `r clim_sens`, `r all_GLS`).
Responses to $DBH$ were as described above (Fig. `r size`).

In general, $DBH$ explained more variation in growth rates than did climate, but its relative importance varied across growth metrics and sites (Figs. `r all_GLS`).
The relative importance of $DBH$ tended to be least for $RW$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. `r GLS_SCBI`).
However, there were exceptions, particularly when $RW$ decreased steeply with $DBH$ (e.g., LT; Fig. `r GLS_LT`).

@@

![**Figure 5 | Examples of climate - DBH interactions for three species at three sites.** Shown are modeled response functions at the minimum and maximum and maximum ends of the $DBH$ range. Other terms in the model are held constant at their median. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/pre_temp_groups_dbh_interactions.png)

>>>>

#Figures
schematic=1
SCBI_example=2
clim_sens=3
interactions_fig = 4 #DBH/climate interactions
size=5
year_fig = 6

@@

@@

### Variation in climate sensitivity with DBH {-#Variation}

@@

![**Figure 4 | Examples of climate - DBH interactions for three species at three sites.** Shown are modeled response functions at the minimum and maximum and maximum ends of the $DBH$ range. Other terms in the model are held constant at their median. Transparent ribbons indicate 95% confidence intervals. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD.](tables_figures/pre_temp_groups_dbh_interactions.png)

When a precipitation variable, a temperature variable, and $DBH$ were all included as candidate variables in the GLS models, typically all three were included in the top model, regardless of the growth metric used.
Climate responses were generally similar to those described above for models without a $DBH$ term, although some of the weaker climate responses were not consistently included in top models (e.g., $T_{min}$ responses at BCNM; Figs. `r clim_sens`, `r all_GLS`).
In general, $DBH$ explained more variation in growth rates than did climate, but its relative importance varied across growth metrics and sites (Figs. `r all_GLS`).
The relative importance of $DBH$ tended to be least for $RW$, intermediate for $BAI$, and highest for $\Delta AGB$ (e.g., at SCBI; Fig. `r GLS_SCBI`).
However, there were exceptions, particularly when $RW$ decreased steeply with $DBH$ (e.g., LT; Fig. `r GLS_LT`).

![**Figure 5 | Growth sensitivity to DBH: (a) $RW$, (b) $BAI$, (c) $\Delta AGB$.** Relationships for species are plotted when included in the top model. Other terms in the model are held constant at their median. Best-fit polynomials are plotted with solid lines when both first- and second-order terms are significant (t-test’s p-value <0.05), dashed lines when only one term is significant, and dotted lines when neither is significant.  Transparent ribbons indicate 95% confidence intervals.](tables_figures/DBH_responses.png)
